COVID19 - Forecast and predictions using a time dependent SEIR model - Italy

### 2020-03-21 draft_analysis_Italy_new.Rmd
Add home page, navigation and theme

```{r echo=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_knit$set(root.dir= normalizePath('..'))
knitr::opts_chunk$set(error = FALSE)
```
---
title: "COVID19 - Forecast and predictions using a time dependent SEIR model - Italy"
author: "Paolo Girardi"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
always_allow_html: yes
---
<a rel="license" href="http://creativecommons.org/licenses/by-nc/4.0/"><img alt="Creative Commons License" style="border-width:0" src="https://i.creativecommons.org/l/by-nc/4.0/88x31.png" /></a><br />This work is licensed under a <a rel="license" href="http://creativecommons.org/licenses/by-nc/4.0/">Creative Commons Attribution-NonCommercial 4.0 International License</a>.

>>>>

---
title: "COVID19 - Forecast and predictions using a time dependent SEIR model - Italy"
author: "Paolo Girardi"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: rmarkdown::github_document
always_allow_html: yes
---
<a rel="license" href="http://creativecommons.org/licenses/by-nc/4.0/"><img alt="Creative Commons License" style="border-width:0" src="https://i.creativecommons.org/l/by-nc/4.0/88x31.png" /></a><br />This work is licensed under a <a rel="license" href="http://creativecommons.org/licenses/by-nc/4.0/">Creative Commons Attribution-NonCommercial 4.0 International License</a>.
